Modelling low Mach number stellar hydrodynamics with MAESTROeX

### 2019-10-03 astronum_2019_MAESTROeX/astronum-maestroex.tex
fix spelling

\begin{abstract}
Modelling long-time convective flows in the interiors of stars is extremeley challenging using conventional compressible hydrodynamics codes due to the acoustic timestep limitation.
Many of these flows are in the low Mach number regime, which allows us to exploit the relationship between acoustic and advective time scales to develop a more computationally efficient approach.
\maestroex\ is an open source low Mach number stellar hydrodynamics code that allows much larger timesteps to be taken, therefore enabling systems to be modelled for much longer periods of time. This is particularly important for the problem of convection in the cores of rotating massive stars prior to core collapse. To fully capture the dynamics, it is necessary to model these systems in three dimensions at high resolution over many rotational periods.  We present an overview of \maestroex's current capabilities, describe ongoing work to incorporate the effects of rotation and discuss how we are optimizing the code to run on GPUs. 
\end{abstract}

>>>>

\begin{abstract}
Modelling long-time convective flows in the interiors of stars is extremely challenging using conventional compressible hydrodynamics codes due to the acoustic timestep limitation.
Many of these flows are in the low Mach number regime, which allows us to exploit the relationship between acoustic and advective time scales to develop a more computationally efficient approach.
\maestroex\ is an open source low Mach number stellar hydrodynamics code that allows much larger timesteps to be taken, therefore enabling systems to be modelled for much longer periods of time. This is particularly important for the problem of convection in the cores of rotating massive stars prior to core collapse. To fully capture the dynamics, it is necessary to model these systems in three dimensions at high resolution over many rotational periods.  We present an overview of \maestroex's current capabilities, describe ongoing work to incorporate the effects of rotation and discuss how we are optimizing the code to run on GPUs. 
\end{abstract}
